What do incoming university students believe about open science practices in

### 2021-11-12 analysis/Manuscript.Rmd
pull out corrs from Table 3 to supplemental table

The remaining `r n` participants were eligible based on starting their first unit 
of study in psychology at a university within the next month. Of the eligible 
participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
`r age [2,2]` reported that they were 25–34 years old, `r age [3,2]` were 35–44 
years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
Most participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender.

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

@@

We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded one norm because it did not refer to externally observable behaviour (critically evaluating published studies vs. accepting them), and we included one practice out of interest (data sharing on request). Participants indicated their estimate on a slider bar ranging from 0% to 100%.

@@

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  dplyr::select(practice, Norm, Counternorm, Difference)

# notes for the correlations....
# just the correlation with CI
# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

#correlation test with CI and p-values in a clean tibble
# critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
# tidy(critical_corr_test)

# use this tutorial to try to get the correlations for each practice (using the long data)
# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html

# join the corr tibble with the means tibble 
practice_means_corr <- practice_means %>% inner_join(corr, by = "practice")

# combine the confidence intervals into one column
practice_means_corr$Correlation <- paste0(practice_means_corr$estimate, 
                            " [",
                            practice_means_corr$conf.low,
                            ", ", 
                            practice_means_corr$conf.high,
                            "]")

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  relocate (practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

practice_means_corr <- practice_means_corr %>% 
  rename(Practice = practice) %>% 
  rename("Correlation p-value" = p.value) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high))

practice_means_corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprint", "Preregistration", "Registered reports")

# need to figure out whether I can rotate a page in papaja
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word. 
# JB: Moving correlations to a supplement will solve the problem I'm trying to resolve anyway...

knitr::kable(practice_means_corr,
             caption = "Means (sd) for norms, counternorms, the difference between norms and counternorms, and correlations between norms and counternorms",
             digits = 2,
             align = c('lccc'))

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->
<!-- JB: I've changed the heading of the p.value column for clarity. If we pull the corrs out
into a new table in the supplemental material, then we will want the p-value with it. -->

@@

in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprint", "Pre-registration", "Registered report")

@@

>>>>

The remaining `r n` participants were eligible based on starting their first unit 
of study in psychology at a university within the next month. Of the eligible 
participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
`r age [2,2]` reported that they were 25–34 years old, `r age [3,2]` were 35–44 
years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
Most participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender. *We still need to fix this...see email from Nov 12th*

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

@@

We also sought to measure participants' normative beliefs about how researchers actually conduct psychological science. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded one norm because it did not refer to externally observable behaviour (critically evaluating published studies vs. accepting them), and we included one practice out of interest (data sharing on request). Participants indicated their estimate on a slider bar ranging from 0% to 100%.

@@

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  rename(Practice = practice) %>% 
  dplyr::select(Practice, Norm, Counternorm, Difference)

practice_means$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered Reports")

knitr::kable(practice_means,
             caption = "Means, standard deviations, and 95% confidence intervals (in square brackets) for norms, counternorms, and the difference between norms and counternorms",
             digits = 2,
             align = c('lccc'))

@@

@@

in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprints", "Pre-registration", "Registered report")

@@

Table A contains the correlations between norms and counternorms, with the 95% confidence intervals and the associated *p*-value.

```{r corrbetweennormandcounternorm}

# use this tutorial to get the correlations for each practice (using the long data)
# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html

# combine the confidence intervals into one column
corr$Correlation <- paste0(corr$estimate, 
                            " [",
                            corr$conf.low,
                            ", ", 
                            corr$conf.high,
                            "]")

# clean up the tibble                          
corr <- corr %>% 
  relocate (p.value, .after = last_col()) %>% 
  rename(Practice = practice) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high))

# reorder the tibble to match the order in Table 3

corr <- corr %>% 
  arrange(match(Practice, c("critical", "hark", "info_for_rep", "open_access", "open_data", "open_materials", "phack", "preprint", "prereg", "reg_report")), desc(Practice))

corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered reports")

knitr::kable(corr,
             caption = "Correlations between norms and counternorms with the 95% confidence intervals (in square brackets) and the associated p-value",
             digits = 2,
             align = c('lccc'))
